\documentclass{article}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{graphics}
\usepackage{color}
\pagestyle{fancy}
\rhead{Steven Seppala, Seth Decker}
\lhead{ECE 440: Networks}
\cfoot{Page : \thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

	\definecolor{dkgreen}{rgb}{0,0.6,0}
	\definecolor{gray}{rgb}{0.5,0.5,0.5}
	\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  %backgroundcolor=\color{dkgreen},
  numbers=left,
  numberstyle=\tiny\color{mauve},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

\begin{document}
\lstset{language=} 

\centering
{
	For our traceroutes we used a UNM computer attached to the ECE server.\\
	\\
	\\
}
\begin{enumerate}
	\item The three traceroutes show similar routes up to line 7. The lines
			up to seven are most likely the network from our host network to the
			access ISP. The packets are then sent to either regional ISPs, tier 1
			ISPs or content delivery networks.

	\item The default maximum number of hops for the traceroute command is
			30. Both presidencia.gob.ve and jnto.go.jp take longer than 30 hops.
			We tried increasing the number of hops to the maximum value 255 and it
			still did not respond.

	\item presidencia.gob.ve took over 200ms before it stopped responding and
			jnto.go.jp took over 100ms while google.com only took 34ms. There are
			a few reasons why this is. For one, .ve and .jp are Venezuela and
			Japan networks, so there will be a lot of cable that will introduce
			propagation delay. While Venezuela is closer to the US than Japan,
			Japan has a much faster network. Venezuela may not be able to keep up
			the demand that Japan can get due to their infrastructure, which can
			introduce slow downs like queueing delay. Google on the other hand is
			so fast because we connect to one of their content delivery networks
			that are able to handle enormous amount of traffic.
\end{enumerate}

\centering
{	
	Attached below are our trace routes for  presidencia.gob.ve ,  www.jnto.go.jp, and google.com; respectively.\\
}

\lstinputlisting{ve}\\
\lstinputlisting{jp}\\
\lstinputlisting{google}\\

\end{document}
